---
title: "revise_wk4"
output: html_document
---

### Read in data:
考试的时候也要这样写，把网址给copy下来。
Located within the Data folder:

* HDI data from: http://hdr.undp.org/en/indicators/68606#
* Shapefile from: https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-2.688200%2C0.000000%2C1.41 

## Load packages
```{r import library}
library(sf)
library(here)
library(tidyverse)
library(dplyr)
library(janitor)
```

## Read in data
### 在read in 之前记得点开csv看看需不需要其他的操作
```{r read in data}
gen_inq <- read_csv(here::here("Data","Gender Inequality Index (GII).csv"),
                    locale = locale(encoding = "latin1"),
                       na = "..", skip=5)

World <- st_read(here::here("Data","World_Countries_(Generalized)","World_Countries__Generalized_.shp"))
```

## Column names

Select columns we want and change country name to country code, using the `countrycode` package

We could also just join it without this on the country name column 

```{r}
gen_inq_use <- gen_inq%>%
  clean_names()%>%
  select(country,x2010,x2019)%>%
  mutate(diff = x2019-x2010)%>%
  slice(1:189) #after 189 there is no countries
```

## Join

Join the csv to world shape file
```{r}
gen_world <- World %>%
  clean_names()%>%
  left_join(.,
		         gen_inq_use,
		          by = c("country" = "country"))
```

```{r}

```

```{r}

```

