---
title: "revise_wk4_and_wk5"
output: html_document
---

### Read in data:
考试的时候也要这样写，把网址给copy下来。
Located within the Data folder:

* HDI data from: http://hdr.undp.org/en/indicators/68606#
* Shapefile from: https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-2.688200%2C0.000000%2C1.41 

## Load packages
```{r import library}
library(countrycode)
library(tidyverse)
library(here)
library(sf)
library(janitor)
library(plotly)
library(tmap)
library(tmaptools)
```

## Read in data
### 在read in 之前记得点开csv看看需不需要其他的操作
```{r read in data}
gen_inq <- read_csv(here::here("Data","Gender Inequality Index (GII).csv"),
                    locale = locale(encoding = "latin1"),
                       na = "..", skip=5)

World <- st_read(here::here("Data","World_Countries_(Generalized)","World_Countries__Generalized_.shp"))
```

## Column names

Select columns we want and change country name to country code, using the `countrycode` package

We could also just join it without this on the country name column 

```{r}
gen_inq_use <- gen_inq%>%
  clean_names()%>%
  select(country,x2010,x2019)%>%
  mutate(diff = x2019-x2010)%>%
  slice(1:189) #after 189 there is no countries
```

## Join

Join the csv to world shape file
```{r}
gen_world <- World %>%
  clean_names()%>%
  left_join(.,
		         gen_inq_use,
		          by = c("country" = "country"))
```

## week5 homework start here
creating a map
```{r}
gen_world2 <- gen_world %>%
  mutate(summary = case_when(diff>0 ~ "improved",
                             diff==0 ~ "the same",
                            TRUE ~ "worse"))
```

```{r}
tmap_mode("plot")
qtm(gen_world,
    fill="diff")
```
##advanced plot?

```{r}
breaks=c(0.0,0.2,0.4,0.6,0.8,1.0) #自己设置的那个图上scale的间隔
diffbreaks=c(-0.4,-0.3,-0.2,-0.1,0,0.1)


# preserve size not direction like WGS84
gen_world = st_transform(gen_world, crs = "+proj=moll") #把平面的地图变成了球型

# plot each map
tm1 <- tm_shape(gen_world) + 
  tm_polygons("x2019", 
              breaks=breaks,
              palette="PuBu")+
  tm_legend(show=FALSE)+
  tm_layout(frame=FALSE)+
  tm_credits("(a)", position=c(0,0.85), size=1.5)

tm2 <- tm_shape(gen_world) + 
  tm_polygons("x2010",
              breaks=breaks,
              palette="PuBu") + 
  tm_legend(show=FALSE)+
  tm_layout(frame=FALSE)+
  tm_credits("(b)", position=c(0,0.85), size=1.5)

tm3 <- tm_shape(gen_world) + 
  tm_polygons("diff",
              #style="fixed",
              breaks=diffbreaks,
              palette=("Blues"),
               midpoint = NA) + 
  tm_legend(show=FALSE)+
  tm_layout(frame=FALSE)+
  tm_credits("(c)", position=c(0,0.85), size=1.5)

legend <- tm_shape(gen_world) + #就是图标
    tm_polygons("diff",
                 palette=("Blues"),
               midpoint = NA) +
    #tm_scale_bar(position=c(0.2,0.04), text.size=0.6)+
    tm_compass(north=0, position=c(0.6,0.6))+
    tm_layout(legend.only = TRUE, legend.position=c(0.3,0.25),asp=0.1)+
    tm_credits("Mapped data:\nUN Gender Inequality Index\nWorld outline:\nArcGIS Hub 
               ", position=c(0.3,0.2), just="left")+
  tm_shape(gen_world) + 
  tm_polygons("x2019", #这个就是加了2019年的图标
              breaks=breaks,
              palette="PuBu")+
  tm_legend(show=TRUE)+
  tm_layout(legend.only = TRUE, legend.position=c(0.1,0.1),asp=0.1)


# in tmap can't make legends side by side unless use this workaround: 
#https://github.com/r-tmap/tmap/issues/476 
t=tmap_arrange(tm1, tm2, tm3, legend, ncol=2)
t
```

